Details of specific functions

### 2022-02-11 inst/gitbook/03_specific-tutorials.Rmd
finished covar bit (very brief)

```{r}
par(mfrow = c(2,2))
## The traitspace
covar.plot(my_covar, col = c("orange", "darkgreen", "blue"), main = "Trait space")
## The traitspace's variance-covariance mean ellipses
covar.plot(my_covar, col = c("orange", "darkgreen", "blue", "grey"), main = "Mean VCV ellipses",
           points = FALSE, ellipses = mean) 
## The traitspace's variance-covariance mean ellipses
covar.plot(my_covar, col = c("orange", "darkgreen", "blue", "grey"), main = "Mean major axes",
           points = FALSE, major.axes = mean)
## A bit of everything
covar.plot(my_covar, col = c("orange", "darkgreen", "blue", "grey"), main = "Ten random VCV matrices",
           points = TRUE, major.axes = TRUE, points.cex = 1/3, n = 10, ellipses = TRUE)
```

@@

`as.covar`

#### Elaborations and explorations

But see probably paper

Finally there are other tools for manipulating MCMCglmm objects. See other [MCMCglmm utilities](#MCMCglmm-utilities)

>>>>

```{r}
par(mfrow = c(2,2))
## The traitspace
covar.plot(my_covar, col = c("orange", "darkgreen", "blue"), main = "Trait space")
## The traitspace's variance-covariance mean ellipses
covar.plot(my_covar, col = c("orange", "darkgreen", "blue", "grey"), main = "Mean VCV ellipses",
           points = FALSE, ellipses = mean) 
## The traitspace's variance-covariance mean ellipses
covar.plot(my_covar, col = c("orange", "darkgreen", "blue", "grey"), main = "Mean major axes",
           points = FALSE, major.axes = mean)
## A bit of everything
covar.plot(my_covar, col = c("orange", "darkgreen", "blue", "grey"), main = "Ten random VCV matrices",
           points = TRUE, major.axes = TRUE, points.cex = 1/3, n = 10, ellipses = TRUE, legend = TRUE)
```

@@

You can then calculate disparity on the `"dispRity"` object like shown previously.
For example, you can get the variances of the groups that where used in the model by using the normal `dispRity` function:

```{r}
summary(dispRity(my_covar, metric = variances))
```

However this is not applied on the variance-covariance matrices from the posteriors of the `MCMCglmm`.
To do that, you need to modify the metric to be recognised as a "covar" metric using the `as.covar` function.
This function transforms any disparity metric (or disparity metric style function) to be applied to the `$covar` part of a `"dispRity"` object.
Basically this `$covar` part is a list containing, for each posterior sample `$VCV`, the variance-covariance matrix and `$loc`, it's optional location in the traitspace.

```{r}
## The first variance covariance matrix for the "gulls" group
my_covar$covar[["gulls"]][[1]]
```

And this is how `as.covar` modifies the disparity metric:

```{r}
## Using the variances function on a VCV matrix
variances(my_covar$covar[["gulls"]][[1]]$VCV)

## The same but using it as a covar metric
as.covar(variances)(my_covar$covar[["gulls"]][[1]])

## The same but applied to the dispRity function
summary(dispRity(my_covar, metric = as.covar(variances)))
```
